FinalManuscript_DISCS_UG

### 2018-07-15 parts/01_introduction_01contextofstudy.tex
More revisions

Digital data privacy and security is a growing concern in various fields, such as cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, and has an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key \cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.

However, research has also considered homomorphic cryptosystems, which not only allow the secure transmission of data, but also allow computations with encrypted data. In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure \cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

>>>>

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, and has an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.

However, research has also considered homomorphic cryptosystems, which not only allow the secure transmission of data, but also allow computations with encrypted data. In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

### 2018-07-15 parts/01_introduction_03objectives.tex
More revisions

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in \cite{li_elliptic_2012, hutchison_fully_2010}. Our study aims to provide an objective comparison of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.

Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time \cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed \cite{li_elliptic_2012}. Finally, as data security is the primary purpose of cryptosystems, we want to evaluate the security of homomorphic cryptosystems as image encryption schemes.

>>>>

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in~\cite{li_elliptic_2012, hutchison_fully_2010}. Our study aims to provide an objective comparison of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.

Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed~\cite{li_elliptic_2012}. Finally, as data security is the primary purpose of cryptosystems, we want to evaluate the security of homomorphic cryptosystems as image encryption schemes.

### 2018-07-15 parts/01_introduction_05scopeandlimitations.tex
More revisions

We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings \cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universal average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both greyscale and color images will be used in the study.

>>>>

We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry~\cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis
        \begin{enumerate}
            \item Number of Pixel Change Rate (NPCR)
            \item Universal Average Change Intensity (UACI)
        \end{enumerate}
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both grayscale and color images will be used in the study.

### 2018-07-15 parts/02_relatedliterature_02commonimageprocessingoperations.tex
More revisions

\subsection{Intensity Transformation}
To define an intensity transformation on an image $I$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $A$. Examples of intensity transformations are image negation, log transformation, and power-law transformation.

@@

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$. This is especially useful since many image capture and output devices such as cameras, printers and displays follow a similar power law to relate physical percieved light intensity and digital pixel intensity values. A power-law transformation defined by the above equation can calibrate the operation on these devices in a process called \textit{gamma correction}. This ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.

In the CrytoImg software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem \cite{ziad_cryptoimg}. To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we aim to investigate the overhead required to approximate these functions.

@@

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
    \caption{(a) A sample image $R$. (b) A sample kernel $k$.}
    \label{fig:spatialfilter}
\end{figure*}
For example, using the image and kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ as follows:
\begin{align*}
	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) +\\
	&(0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) +\\
	&(0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
	&= 223.
\end{align*}
Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the CryptoImg library \cite{ziad_cryptoimg}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

@@

There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening \cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}
% Should I put a table of other kernels too?

>>>>

\subsection{Intensity Transformation}
To define an intensity transformation on an image $R$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$. Examples of intensity transformations are image negation, log transformation, and power-law transformation.

@@

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$. This is especially useful since many image capture and output devices such as cameras, printers and displays follow a similar power law to relate physical perceived light intensity and digital pixel intensity values. A power-law transformation defined by the above equation can calibrate the operation on these devices in a process called \textit{gamma correction}. This ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.

In the \textit{CryptoImg} software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we aim to investigate the overhead required to approximate these functions.

@@

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
    \caption{(a) A sample image $R$. (b) A sample kernel $k$.}
    \label{fig:spatialfilter}
\end{figure*}
For example, using the image and kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ as follows:
\begin{align*}
	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
	&= 223.
\end{align*}
Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

@@

There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}
% Should I put a table of other kernels too?
